Visualization and analysis of probability distributions of large temporal data

### 2021-11-05 Rmd/05-conclusion.Rmd
software development section

This thesis focuses on integrating research approaches into open source R packages such as **gravitas**, **hakear**, and **gracsr**.

@@

The **gravitas** package provides very general tools to compute and manipulate cyclic granularities, and to generate plots displaying distributions conditional on those granularities. It can be utilized in non-temporal cases for which a hierarchical structure can be construed similar to time. It is on CRAN. The website (<https://sayani07.github.io/gravitas>) includes full documentation and two vignettes about the package usage.  There has been a grand total of 12K downloads from the RStudio mirror dating from 2020-11-01 to 2021-11-01.

@@

The open-source R package `hakear` is available on Github (https://github.com/Sayani07/hakear) to implement ideas presented in Chapter \@ref(ch:hakear). Given a `tsibble` and context granularities of interest, the function `wpd()` provides support for computing the wpd for each cyclic granularities or pair of granularities and `select_harmonies()` chooses the ones with significant patterns and ranks them from highest to lowest wpd.

@@

The open-source R package `gracsr` is available on Github (https://github.com/Sayani07/gracsr) to implement ideas presented in Chapter \@ref(ch:gracsr). The package provides functions to carry out the entire clustering methodology discussed in the paper. It is still a work in progress and has won the ACEMS Business Analytics Prize 2021 with a prize money of AUD 3000, which would be utilized in polishing this package and preparing it for CRAN.

>>>>

This thesis focuses on integrating research approaches into open source R packages for reproducibility and ease of use in other applications. So a significant amount of work has been devoted to the development of R packages  **gravitas**, **hakear**, and **gracsr**, each of which correspond to a chapter presented in this thesis.

@@

The **gravitas** package provides very general tools to compute and manipulate cyclic granularities and generate plots displaying distributions conditional on those granularities. The functions `search_gran()`, `create_gran()`, `harmony()`, `gran_advice()` and `prob_plot()` provides a workflow for an analyst to systematically explore large quantities of temporal data across different harmonies (pairs of granularities that can be analyzed together.) This package was developed as part of my internship at Google Summer of Code, 2019. It and has been on CRAN since January 2020. The website (<https://sayani07.github.io/gravitas>) includes full documentation and two vignettes about the package usage. There has been a total of 12K downloads from the RStudio mirror dating from 2020-11-01 to 2021-11-01. This package supplements the paper corresponding to \@ref(ch:gravitas), which has won the ACEMS Business Analytics Award 2021. The package can be generalized to non-temporal applications for which a hierarchical structure can be construed similar to time.

@@

The R package hakear (https://github.com/Sayani07/hakear) implements ideas presented in Chapter @ref (ch:hakear). The function wpd() computes the weighted pairwise distances ($wpd$) for each cyclic granularity or pair of granularities, and select harmonies() selects the ones with significant patterns and ranks them from highest to lowest $wpd$. These selected harmonies can be plotted using package `gravitas` for potentially interesting displays.
Because $wpd$ is computationally expensive, this package uses the R package `parallel` to handle parallel computations.

@@

The open-source R package `gracsr` is available on Github (https://github.com/Sayani07/gracsr) to implement ideas presented in Chapter \@ref(ch:gracsr). The package contains functions for implementing the complete clustering methodology with choices of scaling and distance metrics discussed in the paper. It has received an AUD 3000 grant as part of the ACEMS Business Analytics Prize towards polishing the functions and preparing it for CRAN.
